Optimal updating factor in adaptive flat-distribution-sampling simulations

### 2016-04-22 doc/invt.tex
small changes

We tested the above theory on a model system,
which is to be described in Sec. \ref{sec:results_system}.
%
First, we verify the method of computing errors
using an analytically simple schedule
in Sec. \ref{sec:results_invt}.
%
We then study the optimal schedule from
Eq. \eqref{eq:q_opt}
in Sec. \ref{sec:results_optschedule}.
%
Finally, we compare the Gaussian and
bandpass schemes of different widths
in Sec. \ref{sec:results_cmpschemes}.

@@

We first studied the inverse-time schedule,
%
\begin{equation}
\alpha(t) = \frac{1}{\lambda \, (t + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
where $\lambda$ is a free parameter,
and $t_0 = 2/(\lambda \, \alpha_0)$.
%
The error of this schedule
can be computed analytically
(cf. Appendix \ref{sec:invt_schedule}),
and tested against simulation.

@@

As an example of the multiple-bin schemes,
we chose the nearest-neighbor updating scheme
described in Sec. \ref{sec:nnscheme}.
%
We chose $\mu_1 = 0.24$ to make the smallest eigenvalue
close to zero.
%
Again, simulation and theory agreed well,
as shown in Fig. \ref{fig:errnnbr}.
%
The optimal value of $1/\lambda$,
increased with the simulation length, $T$,
in the global sampling case
(cf. Appendix \ref{sec:invt_deplength}).
%
However, the shift was suppressed
for the local sampling case,
with the optimal $\lambda$ remained around $1.0$
[cf. Eq. \eqref{eq:lambda_nn_onestep}].

>>>>

We tested the above theory on a model system
described in Sec. \ref{sec:results_system}.
%
First, we verify the method of computing errors
%using an inverse-time schedule
in Sec. \ref{sec:results_invt}.
%
We then study the optimal schedule from
Eq. \eqref{eq:q_opt}
in Sec. \ref{sec:results_optschedule}.
%
Finally, we compare the Gaussian and
bandpass updating schemes %of different widths
in Sec. \ref{sec:results_cmpschemes}.

@@

We first tested the theory of computing errors
on the simple inverse-time schedule,
%
\begin{equation}
\alpha(t) = \frac{1}{\lambda \, (t + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
where $\lambda$ is a free parameter,
and $t_0 = 2/(\lambda \, \alpha_0)$.
%
The error of this schedule
can be computed analytically
(cf. Appendix \ref{sec:invt_schedule}),
and tested against simulation.

@@

As an example of multiple-bin schemes,
we tested the nearest-neighbor updating scheme
described in Sec. \ref{sec:nnscheme},
%
with
$\mu_1 = 0.24$ to make the smallest eigenvalue
close to zero.
%
Again, simulation and theory agreed well,
as shown in Fig. \ref{fig:errnnbr}.
%
The optimal value of $1/\lambda$,
increased with the simulation length, $T$,
in the global sampling case
(cf. Appendix \ref{sec:invt_deplength}).
%
However, the shift was suppressed
for the local sampling case,
with the optimal $\lambda$ remained around $1.0$
[cf. Eq. \eqref{eq:lambda_nn_onestep}].
